---
title: "Bayesian Network- What We Learned"
format: revealjs
css: style.css
---

## Introduction

```{r, child='Slide_Maxime_1.qmd'}

```

## Introduction (Part II-a)

```{r, child='Slide_Maxime_2.qmd'}

```

## Introduction (Part II-b)

```{r, child='Slide_Maxime_2bis.qmd'}

```

## Introduction (Part III)

```{r, child='Slide_Maxime_3.qmd'}

```

## Methodology Used 

```{r, child='Slide_Michael_1.qmd'}

```

## Methodology Used (Part II)

```{r, child='Slide_Michael_2.qmd'}



```
## Methodology Used (Part III)

```{r, child='Slide_Michael_3.qmd'}



```
## Methodology Result

```{r, child='Slide_Michael_4.qmd'}



```
## Data Exploration and Analysis

__Key Findings in Income Distribution – Graph Explorations__
```{r, child='Slide_Seth_1.qmd'}

```
## Data Exploration and Analysis (Part II)

__Age and Education Impact on Income__
```{r, child='Slide_Seth_2.qmd'}

```
## Data Exploration and Analysis (Part III)

__Gender and Occupation - Impact on Income__
```{r, child='Slide_Seth_3.qmd'}

```
## Study Overview:

```{r, child='Slide_Sara_1.qmd'}

```

## Main Outcomes:

```{r, child='Slide_Sara_2.qmd'}

```

## Main Outcomes (Part II):

```{r, child='Slide_Sara_3.qmd'}

```
## Conclusion

```{r, child='Slide_Sara_4.qmd'}

```